Identification and performance of stock-recruitment functions in state

### 2024-02-06 Ecov_study/recruitment_functions/presentation/SRR_presentation.Rmd

## OM factors and simulated data examples

<!-- -- example chunk to include figure from file -->
```{r, echo=FALSE, message=FALSE, warnings=FALSE, out.width='50%', fig.align='center'}
 knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'plots_beta_fix', 'model_probability_beta_fix.png') )
```

- make some plots to illustrate OM inputs and resulting simulated data generated
- looks like i can have multiple bullets below a figure

## Couple of slides for Beta standardization

- greg's plots

@@

- simple bullets above table
- we only have 6 EMs that were considered

@@

em_tib <- as_tibble(df.ems) %>%
  mutate(SR=ifelse(r_mod==2, 'Mean', 'BH')) %>%
  mutate(EM_mod = paste0(SR, "_", ecov_how), EM=seq(1,6))

@@

<!-- ```{r cars, echo = TRUE} -->
<!-- summary(cars) -->
<!-- ``` -->

<!-- ## Slide with Plot -->

<!-- ```{r pressure} -->
<!-- plot(pressure) -->
<!-- ``` -->

>>>>

## OM factors and simulated data examples
```{r,  echo=FALSE, message=FALSE, warnings=FALSE}

df.oms    <- readRDS(file.path(here::here(),"Ecov_study", "recruitment_functions", "inputs", "df.oms.RDS"))

om.table <- cbind( unique(df.oms$Fhist), unique(df.oms$R_sig), unique(df.oms$NAA_cor), unique(df.oms$Ecov_effect), unique(df.oms$Ecov_re_cor), unique(df.oms$obs_error)  )
colnames(om.table) <- c('Fhistory', 'R_sigma', 'R_cor', 'Ecov_effect', 'Ecov_cor', 'Obs_error')
   knitr::kable(om.table)

```
- These levels were combined factorially with 4 stock recruit models (all Beverton-Holt) for 256 different OM
- Factors that did not vary were the observation and process error of the Ecov (bot fixed at 0.1)

## Beverton-Holt functional (1 with no Ecov effect, 3 with effect)

```{r,  echo=FALSE, message=FALSE, warnings=FALSE,  out.height='75%', fig.align='center'}
 knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'paper', 'dRdX_1RdRdx.pdf') )
```

## Beta standardization

```{r,  echo=FALSE, message=FALSE, warnings=FALSE,  out.height='75%', fig.align='center'}
 knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'paper', 'dRdX.pdf') )
```

## Some Example OM Simulated Data (100 data sets for each OM)
- still need to make this

@@

- All OMs used Beverton-Holt stock recruit relationship (SRR)
- For the EMs, we also fit a mean SRR with random effects
- There were 6 total EMs fit to each simulated data set (100) for all 256 OMs 
- 153,600 fitted models X 2 for $\beta$ unstandardized and $\beta$ standardized cases

@@

em_tib <- as_tibble(df.ems) %>%
  mutate(SR=ifelse(r_mod==2, 'Mean', 'BH')) %>%
  mutate(EM_mod = paste0(SR, "_", ecov_how), EM=seq(1,6)) %>%
  rename(Ecov_how=ecov_how, SRR=SR) %>%
  mutate(Ecov=c('None', 'Controlling', 'None', 'Controlling', 'Limiting', 'Masking' )) %>%
  relocate(EM, SRR, Ecov_how, Ecov, EM_mod) %>%
  select(-r_mod)

@@

<!-- <!-- -- example chunk to include figure from file --> -->
<!-- ```{r, echo=FALSE, message=FALSE, warnings=FALSE, out.width='50%', fig.align='center'} -->
<!--  knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'plots_beta_fix', 'model_probability_beta_fix.png') ) -->
<!-- ``` -->
